Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-26 cvpr2018.tex
dataset

\subsection{Dataset}
\textbf{Dataset} We use three datasets for evaluation. \textcolor{red}{Yuanpu address}

\subsection{Evaluation metric}
\textbf{Inception score }

@@

>>>>

\subsection{Dataset}
\textbf{Dataset} 
We evaluate our method extensively using three widely used datasets.  CUB dataset contains 11,788 bird images belonging to one of the 200 different classes. Each image in this dataset is associated with 10 text descriptions. We pre-process the image using the same pipeline proposed in \cite{han2017stackgan}, which crops the birds foreground out to  ensure a object-background ratio greater than 0.75.  The OXford-102 dataset contains 102 different categories of flowers with 8189 images in total. Following the similar experiment setting in \cite{han2017stackgan, reed2016generative}, we split both of these datasets into class-disjoint training and testing sets. Each image in both CUB and Oxford-102 is associated with 10 text descriptions. We also exploit the MS  COCO dataset, which contains a much more broad image category and various backgrounds. We use the training and validation splitting setting provided by the original COCO dataset, resulting to a training set containing 80k images and a validation set with 40k images.  Different from CUB and Oxford-102, each image in COCO has 5 text descriptions. 
For text features, we use the pre-trained text encoder model provided in \cite{reed2016generative}, each text description is encoded into a 1024 vector.
During the training stage, we randomly pick-up a crop view from the original images, and pick 4 image sentence embedding and use the mean as conditioning vector.

\subsection{Evaluation metric}
\textbf{Inception score. }  To evaluate the quality of generated images, we resort to the recently proposed qualitative evaluation measurement "inception score"\cite{improvedGAN},
 \begin{equation}
	IS = \exp(\mathbb{E}_xD_{\bm{KL}}(p(y|\bm{x})||p(y)))
 \end{equation}
 where $\bm{x}$ denotes generated sample images, $y$ the class label, $p(y|\bm{x})$ represents the conditional label distribution calculated by the Inception model\cite{inception}.

@@

\subsubsection{What role does noise play}
